Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-09-13 doc/main_jfm.tex
..and updated main_jfm.tex accordingly
update conclusion

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{Slip.eps}
\includegraphics[width=0.4\textwidth]{Slip2.eps}
\end{center} 
  \caption{\label{figure5} The schematic of the intermonolayer slip over
  time. Taking a shear rate $\chi=0.005$ as an example, we denote the
  mean angle between each particle pair $\theta(t)$ where the angle is
  calculated from the relative position of the particles with respect to
  the JP vesicle's center of mass. The configuration plots have two
  fixed particles marked in yellow and blue and labeled with the
  corresponding time $t=2000$ and $t=9000$. The midplane curve is
  denoted as $\Sigma_M$. We see that the intermonolayer slip is largest
  for large shear rates.}
\end{figure}

To calculate the inter-monolayer friction coefficient for the apposing
JP leaflets, we let
\begin{align}
  b = \frac{\langle F\rangle}{\langle L \rangle \langle U\rangle},
\end{align}
%
where 
\begin{align}
  \langle F\rangle = \left\langle \int_{\mathcal{C}_M} 
    \jump{\ttau \cdot \sigma \cdot \nnu} \,\dif s \right\rangle
\end{align}
is the time-averaged, tangential force along the midplane curve
$\mathcal{C}_m$. The parameters $\langle L\rangle$ and $\langle
U\rangle$ are the time-averaged midplane curve length and intermonolayer
slip velocity, respectively.

We calculate $\langle F\rangle$ by first evaluating the smooth
tangential force along curves a positive distance inside and outside
$\mathcal{C}_m$ respectively, and then interpolating at zero distance to
give a force jump. We have made a slight abuse of language: due to the
problem being two-dimensional, the integral $\langle F\rangle$ is
actually a force density per length which when divided by length gives
the requisite force per area. 
%which when divided by length

@@

This study presents a coarse-grained model for JP vesicles that focuses
on the hydrophobic interactions between coarse-grained lipids and
hydrodynamic interactions. In contrast to molecular dynamic simulations,
the hydrophobic interactions exhibit the self-assembly property of the
lipid bilayer membrane. The proposed energy potential combined with the
mobility problem for rigid body motions captures membrane mechanics
including deformations, stretching modulus, and permeability of a JP
membrane. This work is highly applicable with fields in material science
and condensed matter physics such as Janus
colloids~(\cite{Bradley2017,Mallory2017}) and the setup can be tuned to
match experimental results such as the morphology of colloid
surfactants~(\cite{Bradley2016}).

@@

Our future goals include extending the current framework to a
three-dimensional JP vesicle system. This will require additional
algorithmic implementation including a fast summation method such as the
fast multipole method. Another research direction is to introduce
thermal fluctuations into the model. This will result in Janus particles
that include Brownian motion, and this is critical to understand
membrane diffusion. Finally, a more physical boundary condition for the
HAP model will allow us to draw comparisons between computational and
laboratory experiments.

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=11cm]{Figure5_Wrapper.pdf}\\
%\includegraphics[width=0.5\textwidth]{Slip.eps}\\
\includegraphics[width=0.4\textwidth]{Slip2.eps}
\end{center} 
  \caption{\label{figure5} The schematic of the intermonolayer slip over
  time. Taking a shear rate $\chi=0.005$ as an example, we denote the
  mean angle between each particle pair $\theta(t)$ where the angle is
  calculated from the relative position of the particles with respect to
  the JP vesicle's center of mass. The configuration plots have two
  fixed particles marked in yellow and blue and labeled with the
  corresponding time $t=2000$ and $t=9000$. The midplane curve is
  denoted as $C_M$. We see that the intermonolayer slip is largest
  for large shear rates.}
\end{figure}

To calculate the inter-monolayer friction coefficient for the apposing
JP leaflets, we let
\begin{align}
  b = \frac{\langle F\rangle}{\langle L \rangle \langle U\rangle},
\end{align}
%
where 
\begin{align}
  \langle F\rangle = \left\langle \int_{\mathcal{C}_M} 
    \jump{\ttau \cdot \sigma \cdot \nnu} \,\dif s \right\rangle
\end{align}
is the time-averaged, tangential force along the midplane curve
$\mathcal{C}_M$. The parameters $\langle L\rangle$ and $\langle
U\rangle$ are the time-averaged midplane curve length and intermonolayer
slip velocity, respectively.

We calculate $\langle F\rangle$ by first evaluating the smooth
tangential force along curves a positive distance inside and outside
$\mathcal{C}_M$ respectively, and then interpolating at zero distance to
give a force jump. We have made a slight abuse of language: due to the
problem being two-dimensional, the integral $\langle F\rangle$ is
actually a force density per length which when divided by length gives
the requisite force per area. 
%which when divided by length

@@

This study presents a coarse-grained model for JP vesicles that focuses
on the hydrophobic interactions between coarse-grained lipids and
hydrodynamic interactions. In contrast to molecular dynamic simulations,
the hydrophobic interactions exhibit the self-assembly property of the
lipid bilayer membrane. The proposed energy potential combined with the
mobility problem for rigid body motions captures membrane mechanics
including deformations, stretching modulus, and permeability of a JP
membrane. This work is highly applicable with fields in material science
and condensed matter physics such as Janus
colloids~(\cite{Bradley2017,Mallory2017}) and the setup can be tuned to
match experimental results such as the morphology of colloid
surfactants~(\cite{Bradley2016}). 
%
For instances, with the flexibility of the model, we can manage a specific boundary condition
of particle surfaces based on the chemicals chosen in experiments. This can be an assist to 
study of interparticle interactions and chemical compositions in industry.

@@

Our future goals include extending the current framework to a
three-dimensional JP vesicle system. This will require additional
algorithmic implementation including a fast summation method such as the
fast multipole method. Another research direction is to 
%
include the fluctuating hydrodynamics for Brownian suspensions~(\cite{Bao2018}),
%introduce thermal fluctuations into the model. 
%This will result in Janus particles that include Brownian motion, 
and this is critical to understand membrane diffusion. 
Finally, a more physical boundary condition for the
HAP model will allow us to draw comparisons between computational and
laboratory experiments.
